---
title: "UD_Centroids"
author: "Mark Thompson"
date: "2022-08-12"
output: html_document

```{r setup, include=FALSE}

##################################################################

#	Load	required	packages

#automatic install of packages if they are not installed already
list.of.packages <- c(
"adehabitatLT",
"adehabitatHR",
"stringr",
"rgdal",
"here",
"terra",
"stampr",
"sp",
"sf",
"tmap",
"viridisLite",
"quickPlot",
"ggplot2",
"gdistance",
"geosphere",
"dplyr",
"FSA",
"movecost",
"patchwork"
)

new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]

if(length(new.packages) > 0){
  install.packages(new.packages, dep=TRUE)
}

#loading packages
for(package.i in list.of.packages){
  suppressPackageStartupMessages(
    library(
      package.i, 
      character.only = TRUE
      )
    )
}

```

## Retrieve the Aggregate UD polygons organized by season and by study area (BM and TR)

```{r , echo=FALSE, include = FALSE, message = FALSE, warning = FALSE, results = 'hide', fig.show = 'hide'}

seasonsUD <- list()
season_UDdir <- gsub(".shp",
                    "",
                    dir(here("adeHRoutput_noclip","Seasons")
                    ,pattern=".shp$"))

season_UDdirF <- dir(here("adeHRoutput_noclip","Seasons"),
                 pattern=".shp$",
                 full.names = TRUE)
                    
seasonsUD <- lapply(season_UDdirF,
                  FUN = function(files) {
                    vect(files)
                  })
                  
names(seasonsUD) <- season_UDdir
                                    
## organize each "SpatialPolygonsDataFrame" into a different season
# WI =, CA = Calving, SU = Summer, RU = Rutting

BMWI <- seasonsUD[grepl("BM", names(seasonsUD)) & grepl("WI", names(seasonsUD))]
BMCA <- seasonsUD[grepl("BM", names(seasonsUD)) & grepl("CA", names(seasonsUD))]
BMSU <- seasonsUD[grepl("BM", names(seasonsUD)) & grepl("SU", names(seasonsUD))]
BMRU <- seasonsUD[grepl("BM", names(seasonsUD)) & grepl("RU", names(seasonsUD))]

TRWI <- seasonsUD[grepl("TR", names(seasonsUD)) & grepl("WI", names(seasonsUD))]
TRCA <- seasonsUD[grepl("TR", names(seasonsUD)) & grepl("CA", names(seasonsUD))]
TRSU <- seasonsUD[grepl("TR", names(seasonsUD)) & grepl("SU", names(seasonsUD))]
TRRU <- seasonsUD[grepl("TR", names(seasonsUD)) & grepl("RU", names(seasonsUD))]

```

# Season assignments

```{r , echo=FALSE}

## organize each "SpatialPolygonsDataFrame" into a different season
# WI = Winter, CA = Calving, SU = Summer, RU = Rutting

BMWI <- seasonsUD[grepl("BM", names(seasonsUD)) & grepl("WI", names(seasonsUD))]
BMCA <- seasonsUD[grepl("BM", names(seasonsUD)) & grepl("CA", names(seasonsUD))]
BMSU <- seasonsUD[grepl("BM", names(seasonsUD)) & grepl("SU", names(seasonsUD))]
BMRU <- seasonsUD[grepl("BM", names(seasonsUD)) & grepl("RU", names(seasonsUD))]

TRWI <- seasonsUD[grepl("TR", names(seasonsUD)) & grepl("WI", names(seasonsUD))]
TRCA <- seasonsUD[grepl("TR", names(seasonsUD)) & grepl("CA", names(seasonsUD))]
TRSU <- seasonsUD[grepl("TR", names(seasonsUD)) & grepl("SU", names(seasonsUD))]
TRRU <- seasonsUD[grepl("TR", names(seasonsUD)) & grepl("RU", names(seasonsUD))]

years <- c("2003", "2004", "2005", "2006", "2007", "2008", "2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020", "2021")

BM_sUDs <- list(BMWI, BMCA, BMSU, BMRU)
BM_sUDsn <- c("BMWI", "BMCA", "BMSU", "BMRU")
TR_sUDs <- list(TRWI, TRCA, TRSU, TRRU)
TR_sUDsn <- c("TRWI", "TRCA", "TRSU", "TRRU")

```


# Shapefile Imports and Plot Prep

```{r , echo=FALSE}
BM_sUDsn <- c("BMWI", "BMCA", "BMSU", "BMRU")
TR_sUDsn <- c("TRWI", "TRCA", "TRSU", "TRRU")

QU_All.shp <- vect(paste0(here("Spatial Data"),"/Quintette_Caribou_ProjectArea.shp"))
QU_All.shp <- terra::project(QU_All.shp, crs(BMWI[[1]]))
QU_All_SA.shp <- sf::st_as_sf(QU_All.shp)
QU_All_SA.shp[1,1] <- "HEWTR" ## Differentiate TR from BM

FWA_streams <- vect(paste0(here("Spatial Data","FWA_STREAM_NETWORKS_SP"),"/FWSTRMNTWR_line.shp"))
FWA_streams <- sf::st_as_sf(FWA_streams)
  
bbox_new <- st_bbox(QU_All_SA.shp) # current bounding box

xrange <- bbox_new$xmax - bbox_new$xmin # range of x values
yrange <- bbox_new$ymax - bbox_new$ymin # range of y values

bbox_new[1] <- bbox_new[1] - (0.4 * xrange) # xmin - left
bbox_new[3] <- bbox_new[3] + (0.4 * xrange) # xmax - right
bbox_new[2] <- bbox_new[2] - (0.6 * yrange) # ymin - bottom
bbox_new[4] <- bbox_new[4] + (0.4 * yrange) # ymax - top

bbox_new <- bbox_new %>% st_as_sfc() #

QU_BM.shp <- vect(paste0(here("Spatial Data"),"/Quintette_Study_Areas_BM_Dataclip.shp"))
QU_BM_SA.shp <- sf::st_as_sf(QU_BM.shp, crs.proj)

## Bounding box for the UD maps
bbox_newBM <- st_bbox(QU_BM_SA.shp) # current bounding box

xrange <- bbox_newBM$xmax - bbox_newBM$xmin # range of x values
yrange <- bbox_newBM$ymax - bbox_newBM$ymin # range of y values

bbox_newBM[1] <- bbox_newBM[1] - (0.5 * xrange) # xmin - left
bbox_newBM[3] <- bbox_newBM[3] + (0.5 * xrange) # xmax - right
bbox_newBM[2] <- bbox_newBM[2] - (0.5 * yrange) # ymin - bottom
bbox_newBM[4] <- bbox_newBM[4] + (0.5 * yrange) # ymax - top

bbox_newBM <- bbox_newBM %>% st_as_sfc() # take the bounding box ...

## Bounding box for the UD centroid maps - slightly larger on bottom

bbox_newBMc <- st_bbox(QU_BM_SA.shp) # current bounding box

xrange <- bbox_newBMc$xmax - bbox_newBMc$xmin # range of x values
yrange <- bbox_newBMc$ymax - bbox_newBMc$ymin # range of y values

bbox_newBMc[1] <- bbox_newBMc[1] - (0.5 * xrange) # xmin - left
bbox_newBMc[3] <- bbox_newBMc[3] + (0.6 * xrange) # xmax - right
bbox_newBMc[2] <- bbox_newBMc[2] - (0.6 * yrange) # ymin - bottom
bbox_newBMc[4] <- bbox_newBMc[4] + (0.6 * yrange) # ymax - top

bbox_newBMc <- bbox_newBMc %>% st_as_sfc() # take the bounding box ...

##

QU_TR.shp <- vect(paste0(here("Spatial Data"),"/Quintette_Study_Areas_TR_Dataclip.shp"))
QU_TR_SA.shp <- sf::st_as_sf(QU_TR.shp, crs.proj)

## Bounding box for the UD maps
bbox_newTR <- st_bbox(QU_TR_SA.shp) # current bounding box

xrange <- bbox_newTR$xmax - bbox_newTR$xmin # range of x values
yrange <- bbox_newTR$ymax - bbox_newTR$ymin # range of y values

bbox_newTR[1] <- bbox_newTR[1] - (3.0 * xrange) # xmin - left
bbox_newTR[3] <- bbox_newTR[3] + (2.8 * xrange) # xmax - right
bbox_newTR[2] <- bbox_newTR[2] - (3.0 * yrange) # ymin - bottom
bbox_newTR[4] <- bbox_newTR[4] + (2.8 * yrange) # ymax - top

bbox_newTR <- bbox_newTR %>% st_as_sfc() # take the bounding box ..

## Bounding box for the UD centroid maps - These tracks go further, need a larger box
bbox_newTRc <- st_bbox(QU_TR_SA.shp) # current bounding box

xrange <- bbox_newTRc$xmax - bbox_newTRc$xmin # range of x values
yrange <- bbox_newTRc$ymax - bbox_newTRc$ymin # range of y values

bbox_newTRc[1] <- bbox_newTRc[1] - (1.4 * xrange) # xmin - left
bbox_newTRc[3] <- bbox_newTRc[3] + (0.9 * xrange) # xmax - right
bbox_newTRc[2] <- bbox_newTRc[2] - (1.7 * yrange) # ymin - bottom
bbox_newTRc[4] <- bbox_newTRc[4] + (0.9 * yrange) # ymax - top

bbox_newTRc <- bbox_newTRc %>% st_as_sfc() # take the bounding box ..

## Wrapper base layer

sUDsn <- c("WI", "CA", "RU", "SU")

for(i in 1:length(TR_sUDsn)){
  assign(paste0("WRbase_",sUDsn[i]),tm_shape(QU_All_SA.shp, bbox = bbox_new) + tm_fill("CH_TYPE_FI", palette=c("wheat2","lightblue1")) + tm_borders() + tm_layout(frame = FALSE, main.title = paste0("Centroids of 50% UDs Tracked by Season: ", sUDsn[i]), legend.show = FALSE)  + tm_scale_bar(position = c("right","top")))
}

## Bullmoose
## Seasonal UD 50% polygons plotted over season by year.
for(i in 1:length(BM_sUDsn)){
    for(y in 1:length(BM_sUDs[[i]])){
      vir_10 <- viridis(n = length(BM_sUDs[[i]]))
      if(y < 9){
      assign(paste0(BM_sUDsn[i],"a",y),(assign(paste0("tmbase_",BM_sUDsn[i],y),tm_shape(QU_BM_SA.shp, bbox = bbox_newBM) + tm_borders() + tm_layout(frame = TRUE, main.title = paste0(BM_sUDsn[[i]], " Year: 200",y+1), main.title.size =0.8)) + assign(paste0(BM_sUDsn[i],y),tm_shape(st_as_sf(BM_sUDs[[i]][[y]])) + tm_layout(frame = TRUE) + tm_polygons(col=vir_10[y], alpha = 0.2))))
      }
      else{
      assign(paste0(BM_sUDsn[i],"a",y),(assign(paste0("tmbase_",BM_sUDsn[i],y),tm_shape(QU_BM_SA.shp, bbox = bbox_newBM) + tm_borders() + tm_layout(frame = TRUE, main.title = paste0(BM_sUDsn[[i]], " Year: 20",y+1), main.title.size =0.8)) + assign(paste0(BM_sUDsn[i],y),tm_shape(st_as_sf(BM_sUDs[[i]][[y]])) + tm_layout(frame = TRUE) + tm_polygons(col=vir_10[y], alpha = 0.2))))
      }
    }
}
 
## The BM base ("tmbase_BMEW"...) - stand alone study area if needed
for(i in 1:length(BM_sUDsn)){
  assign(paste0("tmbase_",BM_sUDsn[i]),tm_shape(QU_BM_SA.shp) + tm_borders())
}

## Trend Roman
## Seasonal UD 50% polygons plotted over season by year.
for(i in 1:length(TR_sUDsn)){
    for(y in 1:length(TR_sUDs[[i]])){
      vir_10 <- viridis(n = length(TR_sUDs[[i]]))
      if(y < 9){
      assign(paste0(TR_sUDsn[i],"a",y),(assign(paste0("tmbase_",TR_sUDsn[i],y),tm_shape(QU_TR_SA.shp, bbox = bbox_newTR) + tm_borders() + tm_layout(frame = TRUE, main.title = paste0(TR_sUDsn[[i]], " Year: 200",y+1), main.title.size =0.8)) + assign(paste0(TR_sUDsn[i],y),tm_shape(st_as_sf(TR_sUDs[[i]][[y]])) + tm_layout(frame = TRUE) + tm_polygons(col=vir_10[y], alpha = 0.2))))
        }
      else{
      assign(paste0(TR_sUDsn[i],"a",y),(assign(paste0("tmbase_",TR_sUDsn[i],y),tm_shape(QU_TR_SA.shp, bbox = bbox_newTR) + tm_borders() + tm_layout(frame = TRUE, main.title = paste0(TR_sUDsn[[i]], " Year: 20",y+1), main.title.size =0.8)) + assign(paste0(TR_sUDsn[i],y),tm_shape(st_as_sf(TR_sUDs[[i]][[y]])) + tm_layout(frame = TRUE) + tm_polygons(col=vir_10[y], alpha = 0.2))))
        
      }
      }
}

```


##Digital Elevation Model

Alos Polsar DEM scanned on June 1, 2006.

```{r, echo=FALSE}

DEM <- rast(paste0(here("Input Data"),"/AP_01870_FBS_F1090_RT1.dem.tif"))
DEM <- project(DEM, crs("EPSG:32610"))

DEM2 <- rast(paste0(here("Input Data"),"/AP_02045_FBS_F1090_RT1.dem.tif"))
DEM2 <- project(DEM2, crs("EPSG:32610"))

DEM <- merge(DEM,DEM2)

DEM3 <- rast(paste0(here("Input Data"),"/AP_01870_FBS_F1080_RT1.dem.tif"))
DEM3 <- project(DEM3, crs("EPSG:32610"))

DEM <- merge(DEM,DEM3)

DEM4 <- rast(paste0(here("Input Data"),"/AP_05575_FBS_F1090_RT1.dem.tif"))
DEM4 <- project(DEM4, crs("EPSG:32610"))

DEM <- merge(DEM,DEM4)

writeRaster(DEM, paste0(here("Input Data"),"/ALOS_DEM_FULL.tif"),overwrite=TRUE, gdal=c("COMPRESS=DEFLATE", "TFW=YES"))
DEM <- rast(paste0(here("Input Data"),"/ALOS_DEM_FULL.tif"))

tcrop <- rast(nrows=5493, ncols=6908, nlyrs=1, xmin=565000, xmax=655000, 
          ymin=6072600, ymax=6131000, crs=crs(DEM),val=1)
          
DEM <- crop(DEM,tcrop)

writeRaster(DEM, paste0(here("Input Data"),"/ALOS_DEM.tif"),overwrite=TRUE, gdal=c("COMPRESS=DEFLATE", "TFW=YES"))

DEM <- rast(paste0(here("Input Data"),"/ALOS_DEM.tif"))

```

## Creating the UD centroids and mapping their linkages through time

```{r , echo=FALSE, include = FALSE, message = FALSE, warning = FALSE, results = 'hide', fig.show = 'hide'}

## Bullmoose
centroidL <- list()
centroidLn <- list()
clc = 1
dcnt = 1
BMUDdist <- data.frame()

for(i in 1:length(BM_sUDsn)){
    for(y in 1:length(BM_sUDs[[i]])){
      centroidL[[clc]] <- st_centroid(st_as_sf(BM_sUDs[[i]][[y]]))
      centroidLn[clc] <- paste0(BM_sUDsn[i],"_",substr(names(BM_sUDs[[i]][y]),8,11),"_centroid")
      
      if(clc > 1){
      dpoints <- rbind(c(as.numeric(st_coordinates(centroidL[[clc]]))),as.numeric(st_coordinates(centroidL[[clc-1]])))
      BMUDdist[dcnt,1] <- pointDistance(dpoints, lonlat=FALSE)[2,1]
      BMUDdist[dcnt,2] <- paste0(centroidLn[clc-1],"_to_",centroidLn[clc])
      dcnt = dcnt + 1
      }
      
      clc = clc + 1
    }
}

colnames(BMUDdist) <- c("dist.m","UDs")
write.csv(BMUDdist, file = paste0(here("Tables"),"/BMUDsCentDistEuclidian.csv"))

centroidLn <- unlist(centroidLn)
BMcentroidL <- centroidL
names(BMcentroidL) <- centroidLn


## Lines between centroids
ctrli <- list()
ctrnm <- list()
clc = 1

for(i in 1:length(BM_sUDsn)){
    for(y in 1:length(BM_sUDs[[i]])){
      if(clc >= length(centroidL)){break()}
      else{
        ctrli[[clc]] <- makeLines(as(BMcentroidL[[clc+1]], "Spatial"), as(BMcentroidL[[clc]], "Spatial"))
        ctrnm[[clc]] <- paste0(BM_sUDsn[i],y,"_caribouTraj")
        clc = clc + 1
        }
    }
}

ctrnm <- unlist(ctrnm)
names(ctrli) <- ctrnm


## Seasonal UD 50% polygon centroids for plotting over season by year with connecting tracks.

cent_nm <- list()
clc = 1

for(i in 1:length(BM_sUDsn)){
  for(y in 1:length(BM_sUDs[[i]])){
    if(y == 1){
      assign(paste0("cen_",BM_sUDsn[i],y), tm_shape(BMcentroidL[[clc]][2]) + tm_symbols(col = "darkgreen", size = 0.3, shape = 17, border.lwd = 1, border.col = "black") + tm_layout(frame = TRUE))
      cent_nm[[clc]] <- paste0("cen_", BM_sUDsn[i],y)
      clc = clc + 1
      next()
    }
    if(y < length(BM_sUDs[[i]])){
      pal <- plasma(length(BM_sUDs[[i]]))
      assign(paste0("cen_",BM_sUDsn[i],y), tm_shape(BMcentroidL[[clc]][2]) + tm_symbols(col = pal[y], size = 0.3, shape = 21, border.lwd = 1, border.col = "black")  + tm_layout(frame = TRUE))
      cent_nm[[clc]] <- paste0("cen_", BM_sUDsn[i],y)
      clc = clc + 1
      next()
    }
    else{
      assign(paste0("cen_",BM_sUDsn[i],y), tm_shape(BMcentroidL[[clc]][2]) + tm_symbols(col = "red2", size = 0.3, shape = 23, border.lwd = 1, border.col = "black") + tm_layout(frame = TRUE))
      cent_nm[[clc]] <- paste0("cen_", BM_sUDsn[i],y)
      clc = clc + 1
      #next()
    }
  }
}

cent_nm <- unlist(cent_nm)

## Putting the different seasons of lines in their own separate list so the years can be counted
lindf <- list()

for(n in 1:length(BM_sUDsn)){
  assign(paste0("lin_",BM_sUDsn[n]), ctrli[grep(BM_sUDsn[n], names(ctrli))])
  lindf[[n]] <- paste0("lin_",BM_sUDsn[n])
}

lindf <- unlist(lindf)

## Each season has to be looped separately
## BMWI
lines <- list()
clc = 1

for(i in 1:length(lin_BMWI)){
    assign(paste0("cenli_BMWI_",i),tm_shape(lin_BMWI[[i]]) + tm_lines(col="gray28", lwd = 2, lty = "longdash") + tm_layout(frame = TRUE))
    lines[[clc]] <- paste0("cenli_BMWI_",i)
    clc = clc + 1
}
BMEWlines <- unlist(lines)

## BMCA
lines <- list()
clc = 1

for(i in 1:length(lin_BMCA)){
    assign(paste0("cenli_BMCA_",i),tm_shape(lin_BMCA[[i]]) + tm_lines(col="gray28", lwd = 2, lty = "longdash") + tm_layout(frame = TRUE))
    lines[[clc]] <- paste0("cenli_BMCA_",i)
    clc = clc + 1
}
BMCAlines <- unlist(lines)

## BMSU
lines <- list()
clc = 1

for(i in 1:length(lin_BMSU)){
    assign(paste0("cenli_BMSU_",i),tm_shape(lin_BMSU[[i]]) + tm_lines(col="gray28", lwd = 2, lty = "longdash") + tm_layout(frame = TRUE))
    lines[[clc]] <- paste0("cenli_BMSU_",i)
    clc = clc + 1
}
BMSUlines <- unlist(lines)

## BMRU
lines <- list()
clc = 1

for(i in 1:length(lin_BMRU)){
    assign(paste0("cenli_BMRU_",i),tm_shape(lin_BMRU[[i]]) + tm_lines(col="gray28", lwd = 2, lty = "longdash") + tm_layout(frame = TRUE))
    lines[[clc]] <- paste0("cenli_BMRU_",i)
    clc = clc + 1
}
BMRUlines <- unlist(lines)


## Track base layer - Small
for(i in 1:length(BM_sUDsn)){
assign(paste0("Trackbase_",BM_sUDsn[i]),tm_shape(QU_BM_SA.shp, bbox = bbox_newBMc) + tm_fill(col = "bisque4") + tm_borders() + tm_layout(frame = TRUE, main.title = paste0(BM_sUDsn[[i]], " Centroid Track: All Years"), main.title.size =0.8))
}

## cenli short for centroid line
## cen is centroid
centrack_BMWI <- Trackbase_BMWI + cenli_BMWI_1 + cenli_BMWI_2 + cenli_BMWI_3 + cenli_BMWI_4 + cenli_BMWI_5 + cenli_BMWI_6 + cenli_BMWI_7 + cenli_BMWI_8 + cenli_BMWI_9 + cenli_BMWI_10 + cenli_BMWI_11 + cenli_BMWI_12 + cenli_BMWI_13 + cenli_BMWI_14 + cenli_BMWI_15 + cenli_BMWI_16 + cenli_BMWI_17 + cenli_BMWI_18 + cenli_BMWI_19 + cen_BMWI1 + cen_BMWI2 + cen_BMWI3 + cen_BMWI4 + cen_BMWI5 + cen_BMWI6 + cen_BMWI7 + cen_BMWI8 + cen_BMWI9 + cen_BMWI10 + cen_BMWI11 + cen_BMWI12 + cen_BMWI13 + cen_BMWI14 + cen_BMWI15 + cen_BMWI16 + cen_BMWI17 + cen_BMWI18 + cen_BMWI19 + cen_BMWI20

centrack_BMCA <- Trackbase_BMCA + cenli_BMCA_1 + cenli_BMCA_2 + cenli_BMCA_3 + cenli_BMCA_4 + cenli_BMCA_5 + cenli_BMCA_6 + cenli_BMCA_7 + cenli_BMCA_8 + cenli_BMCA_9 + cenli_BMCA_10 + cenli_BMCA_11 + cenli_BMCA_12 + cenli_BMCA_13 + cenli_BMCA_14 + cenli_BMCA_15 + cenli_BMCA_16 + cenli_BMCA_17 + cen_BMCA1 + cen_BMCA2 + cen_BMCA3 + cen_BMCA4 + cen_BMCA5 + cen_BMCA6 + cen_BMCA7 + cen_BMCA8 + cen_BMCA9 + cen_BMCA10 + cen_BMCA11 + cen_BMCA12 + cen_BMCA13 + cen_BMCA14 + cen_BMCA15 + cen_BMCA16 + cen_BMCA17

centrack_BMSU <- Trackbase_BMSU + cenli_BMSU_1 + cenli_BMSU_2 + cenli_BMSU_3 + cenli_BMSU_4 + cenli_BMSU_5 + cenli_BMSU_6 + cenli_BMSU_7 + cenli_BMSU_8 + cenli_BMSU_9 + cenli_BMSU_10 + cenli_BMSU_11 + cenli_BMSU_12 + cenli_BMSU_13 + cenli_BMSU_14 + cenli_BMSU_15 + cenli_BMSU_16 + cenli_BMSU_17 + cen_BMSU1 + cen_BMSU2 + cen_BMSU3 + cen_BMSU4 + cen_BMSU5 + cen_BMSU6 + cen_BMSU7 + cen_BMSU8 + cen_BMSU9 + cen_BMSU10 + cen_BMSU11 + cen_BMSU12 + cen_BMSU13 + cen_BMSU14 + cen_BMSU15 + cen_BMSU16 + cen_BMSU17 + cen_BMSU18

centrack_BMRU <- Trackbase_BMRU + cenli_BMRU_1 + cenli_BMRU_2 + cenli_BMRU_3 + cenli_BMRU_4 + cenli_BMRU_5 + cenli_BMRU_6 + cenli_BMRU_7 + cenli_BMRU_8 + cenli_BMRU_9 + cenli_BMRU_10 + cenli_BMRU_11 + cenli_BMRU_12 + cenli_BMRU_13 + cenli_BMRU_14 + cenli_BMRU_15 + cenli_BMRU_16 + cenli_BMRU_17 + cen_BMRU1 + cen_BMRU2 + cen_BMRU3 + cen_BMRU4 + cen_BMRU5 + cen_BMRU6 + cen_BMRU7 + cen_BMRU8 + cen_BMRU9 + cen_BMRU10 + cen_BMRU11 + cen_BMRU12 + cen_BMRU13 + cen_BMRU14 + cen_BMRU15 + cen_BMRU16 + cen_BMRU17 + cen_BMRU18

```


## Trend Roman centroid movements

```{r , echo=FALSE, include = FALSE, message = FALSE, warning = FALSE, results = 'hide', fig.show = 'hide'}
##Roman
centroidL <- list()
centroidLn <- list()
clc = 1
dcnt = 1
TRUDdist <- data.frame()

for(i in 1:length(TR_sUDsn)){
    for(y in 1:length(TR_sUDs[[i]])){
      centroidL[[clc]] <- st_centroid(st_as_sf(TR_sUDs[[i]][[y]]))
      centroidLn[clc] <- paste0(TR_sUDsn[i],"_",substr(names(TR_sUDs[[i]][y]),8,11),"_centroid")
      if(clc > 1){
        dpoints <- rbind(c(as.numeric(st_coordinates(centroidL[[clc]]))),as.numeric(st_coordinates(centroidL[[clc-1]])))
        TRUDdist[dcnt,1] <- pointDistance(dpoints, lonlat=FALSE)[2,1]
        TRUDdist[dcnt,2] <- paste0(centroidLn[clc-1],"_to_",centroidLn[clc])
        dcnt = dcnt + 1
      }
      clc = clc + 1
    }
}

colnames(TRUDdist) <- c("dist.m","UDs")
write.csv(TRUDdist, file = paste0(here("Tables"),"/TRUDsCentDistEuclidian.csv"))

centroidLn <- unlist(centroidLn)
TRcentroidL <- centroidL
names(TRcentroidL) <- centroidLn


## Lines between centroids
ctrli <- list()
ctrnm <- list()
clc = 1

for(i in 1:length(TR_sUDsn)){
    for(y in 1:length(TR_sUDs[[i]])){
      if(clc >= length(TRcentroidL)){break()}
      else{
        ctrli[[clc]] <- makeLines(as(TRcentroidL[[clc+1]], "Spatial"), as(TRcentroidL[[clc]], "Spatial"))
        ctrnm[[clc]] <- paste0(TR_sUDsn[i],y,"_caribouTraj")
        clc = clc + 1
        }
    }
}

ctrnm <- unlist(ctrnm)
names(ctrli) <- ctrnm


## Seasonal UD 50% polygon centroids plotted over season by year with connecting tracks.

cent_nm <- list()
clc = 1

for(i in 1:length(TR_sUDsn)){
  for(y in 1:length(TR_sUDs[[i]])){
    if(y == 1){
      assign(paste0("cen_",TR_sUDsn[i],y), tm_shape(TRcentroidL[[clc]][2]) + tm_symbols(col = "darkgreen", size = 0.3, shape = 17, border.lwd = 1, border.col = "black") + tm_layout(frame = TRUE))
      cent_nm[[clc]] <- paste0("cen_", TR_sUDsn[i],y)
      clc = clc + 1
      next()
    }
    if(y < length(TR_sUDs[[i]])){
      pal <- plasma(length(TR_sUDs[[i]]))
      assign(paste0("cen_",TR_sUDsn[i],y), tm_shape(TRcentroidL[[clc]][2]) + tm_symbols(col = pal[y], size = 0.3, shape = 21, border.lwd = 1, border.col = "black")  + tm_layout(frame = TRUE))
      cent_nm[[clc]] <- paste0("cen_", TR_sUDsn[i],y)
      clc = clc + 1
      next()
    }
    else{
      assign(paste0("cen_",TR_sUDsn[i],y), tm_shape(TRcentroidL[[clc]][2]) + tm_symbols(col = "red2", size = 0.3, shape = 23, border.lwd = 1, border.col = "black") + tm_layout(frame = TRUE))
      cent_nm[[clc]] <- paste0("cen_", TR_sUDsn[i],y)
      clc = clc + 1
      #next()
    }
  }
}

cent_nm <- unlist(cent_nm)

## Putting the different seasons of lines in their own separate list so the years can be counted
lindf <- list()

for(n in 1:length(TR_sUDsn)){
  assign(paste0("lin_",TR_sUDsn[n]), ctrli[grep(TR_sUDsn[n], names(ctrli))])
  lindf[[n]] <- paste0("lin_",TR_sUDsn[n])
}

lindf <- unlist(lindf)

## Each season has to be looped separately
## TRWI
lines <- list()
clc = 1

for(i in 1:length(lin_TRWI)){
    assign(paste0("cenli_TRWI_",i),tm_shape(lin_TRWI[[i]]) + tm_lines(col="gray28", lwd = 2, lty = "longdash") + tm_layout(frame = TRUE))
    lines[[clc]] <- paste0("cenli_TRWI_",i)
    clc = clc + 1
}
TRWIlines <- unlist(lines)

## TRCA
lines <- list()
clc = 1

for(i in 1:length(lin_TRCA)){
    assign(paste0("cenli_TRCA_",i),tm_shape(lin_TRCA[[i]]) + tm_lines(col="gray28", lwd = 2, lty = "longdash") + tm_layout(frame = TRUE))
    lines[[clc]] <- paste0("cenli_TRCA_",i)
    clc = clc + 1
}
TRCAlines <- unlist(lines)

## TRSU
lines <- list()
clc = 1

for(i in 1:length(lin_TRSU)){
    assign(paste0("cenli_TRSU_",i),tm_shape(lin_TRSU[[i]]) + tm_lines(col="gray28", lwd = 2, lty = "longdash") + tm_layout(frame = TRUE))
    lines[[clc]] <- paste0("cenli_TRSU_",i)
    clc = clc + 1
}
TRSUlines <- unlist(lines)

## TRRU
lines <- list()
clc = 1

for(i in 1:length(lin_TRRU)){
    assign(paste0("cenli_TRRU_",i),tm_shape(lin_TRRU[[i]]) + tm_lines(col="gray28", lwd = 2, lty = "longdash") + tm_layout(frame = TRUE))
    lines[[clc]] <- paste0("cenli_TRRU_",i)
    clc = clc + 1
}
TRRUlines <- unlist(lines)

## Track base layer

for(i in 1:length(TR_sUDsn)){
assign(paste0("Trackbase_",TR_sUDsn[i]),tm_shape(QU_TR_SA.shp, bbox = bbox_newTRc) + tm_fill(col="lightblue1") + tm_borders() + tm_layout(frame = TRUE, main.title = paste0(TR_sUDsn[[i]], " Centroid Track: All Years"), main.title.size =0.5))
}

## cenli short for centroid line
## cen is centroid
centrack_TRWI <- Trackbase_TRWI + cenli_TRWI_1 + cenli_TRWI_2 + cenli_TRWI_3 + cenli_TRWI_4 + cenli_TRWI_5 + cenli_TRWI_6 + cenli_TRWI_7 + cenli_TRWI_8 + cenli_TRWI_9 + cenli_TRWI_10 + cenli_TRWI_11 + cenli_TRWI_12 + cenli_TRWI_13 + cenli_TRWI_14 + cenli_TRWI_15 + cen_TRWI1 + cen_TRWI2 + cen_TRWI3 + cen_TRWI4 + cen_TRWI5 + cen_TRWI6 + cen_TRWI7 + cen_TRWI8 + cen_TRWI9 + cen_TRWI10 + cen_TRWI11 + cen_TRWI12 + cen_TRWI13 + cen_TRWI14 + cen_TRWI15 + cen_TRWI16

centrack_TRCA <- Trackbase_TRCA + cenli_TRCA_1 + cenli_TRCA_2 + cenli_TRCA_3 + cenli_TRCA_4 + cenli_TRCA_5 + cenli_TRCA_6 + cenli_TRCA_7 + cenli_TRCA_8 + cenli_TRCA_9 + cenli_TRCA_10 + cenli_TRCA_11 + cenli_TRCA_12 + cenli_TRCA_13 + cenli_TRCA_14 + cen_TRCA1 + cen_TRCA2 + cen_TRCA3 + cen_TRCA4 + cen_TRCA5 + cen_TRCA6 + cen_TRCA7 + cen_TRCA8 + cen_TRCA9 + cen_TRCA10 + cen_TRCA11 + cen_TRCA12 + cen_TRCA13 + cen_TRCA14 + cen_TRCA15

centrack_TRSU <- Trackbase_TRSU + cenli_TRSU_1 + cenli_TRSU_2 + cenli_TRSU_3 + cenli_TRSU_4 + cenli_TRSU_5 + cenli_TRSU_6 + cenli_TRSU_7 + cenli_TRSU_8 + cenli_TRSU_9 + cenli_TRSU_10 + cenli_TRSU_11 + cenli_TRSU_12 + cenli_TRSU_13 + cenli_TRSU_14 + cen_TRSU1 + cen_TRSU2 + cen_TRSU3 + cen_TRSU4 + cen_TRSU5 + cen_TRSU6 + cen_TRSU7 + cen_TRSU8 + cen_TRSU9 + cen_TRSU10 + cen_TRSU11 + cen_TRSU12 + cen_TRSU13 + cen_TRSU14 + cen_TRSU15

centrack_TRRU <- Trackbase_TRRU + cenli_TRRU_1 + cenli_TRRU_2 + cenli_TRRU_3 + cenli_TRRU_4 + cenli_TRRU_5 + cenli_TRRU_6 + cenli_TRRU_7 + cenli_TRRU_8 + cenli_TRRU_9 + cenli_TRRU_10 + cenli_TRRU_11 + cenli_TRRU_12 + cenli_TRRU_13 + cen_TRRU1 + cen_TRRU2 + cen_TRRU3 + cen_TRRU4 + cen_TRRU5 + cen_TRRU6 + cen_TRRU7 + cen_TRRU8 + cen_TRRU9 + cen_TRRU10 + cen_TRRU11 + cen_TRRU12 + cen_TRRU13 + cen_TRRU14

```

### Enlarged areas
```{r , echo=FALSE}
centrack_Agg_WI <- WRbase_WI + cenli_BMWI_1 + cenli_BMWI_2 + cenli_BMWI_3 + cenli_BMWI_4 + cenli_BMWI_5 + cenli_BMWI_6 + cenli_BMWI_7 + cenli_BMWI_8 + cenli_BMWI_9 + cenli_BMWI_10 + cenli_BMWI_11 + cenli_BMWI_12 + cenli_BMWI_13 + cenli_BMWI_14 + cenli_BMWI_15 + cenli_BMWI_16 + cenli_BMWI_17 + cenli_BMWI_18 + cenli_BMWI_19 + cen_BMWI1 + cen_BMWI2 + cen_BMWI3 + cen_BMWI4 + cen_BMWI5 + cen_BMWI6 + cen_BMWI7 + cen_BMWI8 + cen_BMWI9 + cen_BMWI10 + cen_BMWI11 + cen_BMWI12 + cen_BMWI13 + cen_BMWI14 + cen_BMWI15 + cen_BMWI16 + cen_BMWI17 + cen_BMWI18 + cen_BMWI19 + cen_BMWI20 + cenli_TRWI_1 + cenli_TRWI_2 + cenli_TRWI_3 + cenli_TRWI_4 + cenli_TRWI_5 + cenli_TRWI_6 + cenli_TRWI_7 + cenli_TRWI_8 + cenli_TRWI_9 + cenli_TRWI_10 + cenli_TRWI_11 + cenli_TRWI_12 + cenli_TRWI_13 + cenli_TRWI_14 + cenli_TRWI_15 + cenli_TRWI_16 + cen_TRWI1 + cen_TRWI2 + cen_TRWI3 + cen_TRWI4 + cen_TRWI5 + cen_TRWI6 + cen_TRWI7 + cen_TRWI8 + cen_TRWI9 + cen_TRWI10 + cen_TRWI11 + cen_TRWI12 + cen_TRWI13 + cen_TRWI14 + cen_TRWI15 + cen_TRWI16

centrack_Agg_CA <- WRbase_CA + cenli_BMCA_1 + cenli_BMCA_2 + cenli_BMCA_3 + cenli_BMCA_4 + cenli_BMCA_5 + cenli_BMCA_6 + cenli_BMCA_7 + cenli_BMCA_8 + cenli_BMCA_9 + cenli_BMCA_10 + cenli_BMCA_11 + cenli_BMCA_12 + cenli_BMCA_13 + cenli_BMCA_14 + cenli_BMCA_15 + cenli_BMCA_16 + cen_BMCA1 + cen_BMCA2 + cen_BMCA3 + cen_BMCA4 + cen_BMCA5 + cen_BMCA6 + cen_BMCA7 + cen_BMCA8 + cen_BMCA9 + cen_BMCA10 + cen_BMCA11 + cen_BMCA12 + cen_BMCA13 + cen_BMCA14 + cen_BMCA15 + cen_BMCA16 + cen_BMCA17 + cenli_TRCA_1 + cenli_TRCA_2 + cenli_TRCA_3 + cenli_TRCA_4 + cenli_TRCA_5 + cenli_TRCA_6 + cenli_TRCA_7 + cenli_TRCA_8 + cenli_TRCA_9 + cenli_TRCA_10 + cenli_TRCA_11 + cenli_TRCA_12 + cenli_TRCA_13 + cenli_TRCA_14 + cenli_TRCA_15 + cen_TRCA1 + cen_TRCA2 + cen_TRCA3 + cen_TRCA4 + cen_TRCA5 + cen_TRCA6 + cen_TRCA7 + cen_TRCA8 + cen_TRCA9 + cen_TRCA10 + cen_TRCA11 + cen_TRCA12 + cen_TRCA13 + cen_TRCA14 + cen_TRCA15

centrack_Agg_SU <- WRbase_SU + cenli_BMSU_1 + cenli_BMSU_2 + cenli_BMSU_3 + cenli_BMSU_4 + cenli_BMSU_5 + cenli_BMSU_6 + cenli_BMSU_7 + cenli_BMSU_8 + cenli_BMSU_9 + cenli_BMSU_10 + cenli_BMSU_11 + cenli_BMSU_12 + cenli_BMSU_13 + cenli_BMSU_14 + cenli_BMSU_15 + cenli_BMSU_16 + cenli_BMSU_17 + cen_BMSU1 + cen_BMSU2 + cen_BMSU3 + cen_BMSU4 + cen_BMSU5 + cen_BMSU6 + cen_BMSU7 + cen_BMSU8 + cen_BMSU9 + cen_BMSU10 + cen_BMSU11 + cen_BMSU12 + cen_BMSU13 + cen_BMSU14 + cen_BMSU15 + cen_BMSU16 + cen_BMSU17 + cen_BMSU18 + cenli_TRSU_1 + cenli_TRSU_2 + cenli_TRSU_3 + cenli_TRSU_4 + cenli_TRSU_5 + cenli_TRSU_6 + cenli_TRSU_7 + cenli_TRSU_8 + cenli_TRSU_9 + cenli_TRSU_10 + cenli_TRSU_11 + cenli_TRSU_12 + cenli_TRSU_13 + cenli_TRSU_14 + cen_TRSU1 + cen_TRSU2 + cen_TRSU3 + cen_TRSU4 + cen_TRSU5 + cen_TRSU6 + cen_TRSU7 + cen_TRSU8 + cen_TRSU9 + cen_TRSU10 + cen_TRSU11 + cen_TRSU12 + cen_TRSU13 + cen_TRSU14 + cen_TRSU15

centrack_Agg_RU <- WRbase_RU + cenli_BMRU_1 + cenli_BMRU_2 + cenli_BMRU_3 + cenli_BMRU_4 + cenli_BMRU_5 + cenli_BMRU_6 + cenli_BMRU_7 + cenli_BMRU_8 + cenli_BMRU_9 + cenli_BMRU_10 + cenli_BMRU_11 + cenli_BMRU_12 + cenli_BMRU_13 + cenli_BMRU_14 + cenli_BMRU_15 + cenli_BMRU_16 + cenli_BMRU_17 + cen_BMRU1 + cen_BMRU2 + cen_BMRU3 + cen_BMRU4 + cen_BMRU5 + cen_BMRU6 + cen_BMRU7 + cen_BMRU8 + cen_BMRU9 + cen_BMRU10 + cen_BMRU11 + cen_BMRU12 + cen_BMRU13 + cen_BMRU14 + cen_BMRU15 + cen_BMRU16 + cen_BMRU17 + cen_BMRU18 + cenli_TRRU_1 + cenli_TRRU_2 + cenli_TRRU_3 + cenli_TRRU_4 + cenli_TRRU_5 + cenli_TRRU_6 + cenli_TRRU_7 + cenli_TRRU_8 + cenli_TRRU_9 + cenli_TRRU_10 + cenli_TRRU_11 + cenli_TRRU_12 + cenli_TRRU_13 + cen_TRRU1 + cen_TRRU2 + cen_TRRU3 + cen_TRRU4 + cen_TRRU5 + cen_TRRU6 + cen_TRRU7 + cen_TRRU8 + cen_TRRU9 + cen_TRRU10 + cen_TRRU11 + cen_TRRU12 + cen_TRRU13 + cen_TRRU14



```

# Mapping

This code chunk organizes figures with Tmap package to arrange the panels.

```{r , echo=FALSE}

BMWI_ps1 <- tmap_arrange(centrack_BMWI, BMWIa1, BMWIa2, BMWIa3, BMWIa4, BMWIa5)
BMWI_ps2 <- tmap_arrange(BMWIa6, BMWIa7, BMWIa8, BMWIa9, BMWIa10, BMWIa11)
BMWI_ps3 <- tmap_arrange(BMWIa12, BMWIa13, BMWIa14, BMWIa15, BMWIa16)
BMWI_ps4 <- tmap_arrange(BMWIa17, BMWIa18)

BMCA_ps1 <- tmap_arrange(centrack_BMCA, BMCAa1, BMCAa2, BMCAa3, BMCAa4, BMCAa5)
BMCA_ps2 <- tmap_arrange(BMCAa6, BMCAa7, BMCAa8, BMCAa9, BMCAa10, BMCAa11)
BMCA_ps3 <- tmap_arrange(BMCAa12, BMCAa13, BMCAa14, BMCAa15, BMCAa16)

BMSU_ps1 <- tmap_arrange(centrack_BMSU, BMSUa1, BMSUa2, BMSUa3, BMSUa4, BMSUa5)
BMSU_ps2 <- tmap_arrange(BMSUa6, BMSUa7, BMSUa8, BMSUa9, BMSUa10, BMSUa11)
BMSU_ps3 <- tmap_arrange(BMSUa12, BMSUa13, BMSUa14, BMSUa15, BMSUa16)

BMRU_ps1 <- tmap_arrange(centrack_BMRU, BMRUa1, BMRUa2, BMRUa3, BMRUa4, BMRUa5)
BMRU_ps2 <- tmap_arrange(BMRUa6, BMRUa7, BMRUa8, BMRUa9, BMRUa10, BMRUa11)
BMRU_ps3 <- tmap_arrange(BMRUa12, BMRUa13, BMRUa14, BMRUa16)


TRWI_ps1 <- tmap_arrange(centrack_TRWI, TRWIa1, TRWIa2, TRWIa3, TRWIa4, TRWIa5)
TRWI_ps2 <- tmap_arrange(TRWIa6, TRWIa7, TRWIa8, TRWIa9, TRWIa10, TRWIa11)
TRWI_ps3 <- tmap_arrange(TRWIa12, TRWIa13, TRWIa14, TRWIa15)

TRCA_ps1 <- tmap_arrange(centrack_TRCA, TRCAa1, TRCAa2, TRCAa3, TRCAa4, TRCAa5)
TRCA_ps2 <- tmap_arrange(TRCAa6, TRCAa7, TRCAa8, TRCAa9, TRCAa10, TRCAa11)
TRCA_ps3 <- tmap_arrange(TRCAa12, TRCAa13, TRCAa14, TRCAa15)

TRSU_ps1 <- tmap_arrange(centrack_TRSU, TRSUa1, TRSUa2, TRSUa3, TRSUa4, TRSUa5)
TRSU_ps2 <- tmap_arrange(TRSUa6, TRSUa7, TRSUa8, TRSUa9, TRSUa10, TRSUa11)
TRSU_ps3 <- tmap_arrange(TRSUa12, TRSUa13, TRSUa14, TRSUa15)

TRRU_ps1 <- tmap_arrange(centrack_TRRU, TRRUa1, TRRUa2, TRRUa3, TRRUa4, TRRUa5)
TRRU_ps2 <- tmap_arrange(TRRUa6, TRRUa7, TRRUa8, TRRUa9, TRRUa10, TRRUa11)
TRRU_ps3 <- tmap_arrange(TRRUa12, TRRUa13, TRRUa14)

pal <- grey.colors(10, start=0.2, end=0.8)
  #viridisLite::cividis(20, begin = 0.3, end = 0.8)
centrack_Agg_WI <- tm_shape(DEM) + tm_raster(style = "cont", palette = pal, legend.show = FALSE) + centrack_Agg_WI
centrack_Agg_CA <- tm_shape(DEM) + tm_raster(style = "cont", palette = pal, legend.show = FALSE) + centrack_Agg_CA
centrack_Agg_SU <- tm_shape(DEM) + tm_raster(style = "cont", palette = pal, legend.show = FALSE) + centrack_Agg_SU
centrack_Agg_RU <- tm_shape(DEM) + tm_raster(style = "cont", palette = pal, legend.show = FALSE) + centrack_Agg_RU

udtrackAgg <- c("centrack_Agg_WI", "centrack_Agg_CA", "centrack_Agg_SU", "centrack_Agg_RU")
udtrackAggli <- list(centrack_Agg_WI, centrack_Agg_CA, centrack_Agg_SU, centrack_Agg_RU)

panels <- c("BMWI_ps1", "BMWI_ps2", "BMWI_ps3", "BMWI_ps4", "BMCA_ps1", "BMCA_ps2", "BMCA_ps3", "BMSU_ps1", "BMSU_ps2", "BMSU_ps3", "BMRU_ps1", "BMRU_ps2", "BMRU_ps3", "TRWI_ps1", "TRWI_ps2", "TRWI_ps3", "TRCA_ps1", "TRCA_ps2", "TRCA_ps3", "TRSU_ps1", "TRSU_ps2", "TRSU_ps3", "TRRU_ps1", "TRRU_ps2", "TRRU_ps3")

panelsl <- list(BMWI_ps1, BMWI_ps2, BMWI_ps3, BMWI_ps4, BMCA_ps1, BMCA_ps2, BMCA_ps3, BMSU_ps1, BMSU_ps2, BMSU_ps3, BMRU_ps1, BMRU_ps2, BMRU_ps3, TRWI_ps1, TRWI_ps2, TRWI_ps3, TRCA_ps1, TRCA_ps2, TRCA_ps3, TRSU_ps1, TRSU_ps2, TRSU_ps3, TRRU_ps1, TRRU_ps2, TRRU_ps3)

for(i in 1:length(panels)){
  tmap_save(panelsl[[i]], paste0(here("Maps"),"/",panels[i],"b.png"), device = ragg::agg_png)
}

for(i in 1:length(udtrackAgg)){
  tmap_save(udtrackAggli[[i]], paste0(here("Maps"),"/",udtrackAgg[i],"b.png"), device = ragg::agg_png)
}

#pdf(BMWE_ps1)
#BMWI_ps1
#dev.off()


#centrack_BMRU
#centrack_TRRU


```

#ploting the areas (km^2) of 50% UDs over time

```{r , echo=FALSE}
BM_sUDs_areas <- list()
p = 1

for(n in 1:length(BM_sUDs)){
  for(y in 1:length(BM_sUDs[[n]])){
    BM_sUDs_areas[p] <- BM_sUDs[[n]][[y]]$area
    names(BM_sUDs_areas[[p]]) <- paste0(BM_sUDsn[n],"_",substr(names(BM_sUDs[[n]][y]), 8, 11))
    p = p+1
  }
}

BM_sUDs_areas <- data.frame(unlist(BM_sUDs_areas))

BM_sUDs_areas$season <- rownames(BM_sUDs_areas)
BM_sUDs_areas$year <- substr(BM_sUDs_areas$season, 6, 9)
BM_sUDs_areas$loc <- substr(BM_sUDs_areas$season, 1, 2)
BM_sUDs_areas$season <- substr(BM_sUDs_areas$season, 3, 4)
colnames(BM_sUDs_areas) <- c("area", "season","year")
rownames(BM_sUDs_areas) <- c(1:nrow(BM_sUDs_areas))
BM_sUDs_areas <- BM_sUDs_areas[, c(3,4,1,2)]
BM_sUDs_areas$year <- as.numeric(BM_sUDs_areas$year)
colnames(BM_sUDs_areas) <- c("year","SA","area","season")

write.csv(BM_sUDs_areas, file = paste0(here("Tables"),"/BM_sUDs_areas.csv"))

pBM = ggplot(BM_sUDs_areas, aes(x = year, y = area, color = season)) +
  geom_line(lwd=2)  + xlab('Years') +
  ylab("Area (ha)") + theme_bw() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size=9)) + theme(panel.grid.major.x = element_blank(),
       panel.grid.minor.x = element_blank()) +
  scale_x_continuous(breaks = seq(min(BM_sUDs_areas$year), max(BM_sUDs_areas$year), by = 1)) +
   ggtitle("Bullmoose 50% UD Core Habitat") + theme(text = element_text(size = 14))

pBM$labels$colour <- "Seasons"


## Two Season plot
winter = "WI"
summer = c("CA","SU","RU")


BM_sUDs_Winterareas <- BM_sUDs_areas[which(BM_sUDs_areas$season == winter),]
BM_sUDs_Winterareas <- aggregate(BM_sUDs_Winterareas["area"],BM_sUDs_Winterareas["year"],sum)
BM_sUDs_Winterareas$season <- "winter"

BM_sUDs_Summerareas <- subset(BM_sUDs_areas,grepl(paste0(summer, collapse = "|"), season))
BM_sUDs_Summerareas <- aggregate(BM_sUDs_Summerareas["area"],BM_sUDs_Summerareas["year"],sum)
BM_sUDs_Summerareas$season <- "summer"

BM_sUDs_WS <- rbind(BM_sUDs_Winterareas,BM_sUDs_Summerareas)

pBM_SumWin = ggplot(BM_sUDs_WS, aes(x = year, y = area, color = season)) +
  geom_line()  + xlab('Years') +
  ylab('Area (km^2)') + theme_bw() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  scale_x_continuous(breaks = seq(min(BM_sUDs_Winterareas$year), max(BM_sUDs_Winterareas$year), by = 1)) +
   ggtitle("Bullmoose 50% UD Seasonal Areas X Year")

pBM_SumWin$labels$colour <- "Season"


## Trend Roman
TR_sUDs_areas <- list()
p = 1

for(n in 1:length(TR_sUDs)){
  for(y in 1:length(TR_sUDs[[n]])){
    TR_sUDs_areas[p] <- TR_sUDs[[n]][[y]]$area
    names(TR_sUDs_areas[[p]]) <- paste0(TR_sUDsn[n],"_",substr(names(TR_sUDs[[n]][y]), 8, 11))
    p = p+1
  }
}

TR_sUDs_areas <- data.frame(unlist(TR_sUDs_areas))

TR_sUDs_areas$season <- rownames(TR_sUDs_areas)
TR_sUDs_areas$year <- substr(TR_sUDs_areas$season, 6, 9)
TR_sUDs_areas$loc <- substr(TR_sUDs_areas$season, 1, 2)
TR_sUDs_areas$season <- substr(TR_sUDs_areas$season, 3, 4)
colnames(TR_sUDs_areas) <- c("area", "season","year")
rownames(TR_sUDs_areas) <- c(1:nrow(TR_sUDs_areas))
TR_sUDs_areas <- TR_sUDs_areas[, c(3,4,1,2)]
TR_sUDs_areas$year <- as.numeric(TR_sUDs_areas$year)
colnames(TR_sUDs_areas) <- c("year","SA","area","season")

write.csv(TR_sUDs_areas, file = paste0(here("Tables"),"/TR_sUDs_areas.csv"))
BMTR_sUDs_areas <- rbind(BM_sUDs_areas, TR_sUDs_areas)
write.csv(BMTR_sUDs_areas, file = paste0(here("Tables"),"/BMTR_sUDs_areas"))

pTR = ggplot(TR_sUDs_areas, aes(x = year, y = area, color = season)) +
  geom_line(lwd=2)  + xlab('Years') +
  ylab("Area (ha)") + theme_bw() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  scale_x_continuous(breaks = seq(min(TR_sUDs_areas$year), max(TR_sUDs_areas$year), by = 1)) +
   ggtitle("Roman 50% UD Core Habitat") + theme(text = element_text(size = 14))

pTR$labels$colour <- "Seasons"


## Two Season plot
winter = "WI"
summer = c("CA","SU","RU")


TR_sUDs_Winterareas <- TR_sUDs_areas[which(TR_sUDs_areas$season == winter),]
TR_sUDs_Winterareas <- aggregate(TR_sUDs_Winterareas["area"],TR_sUDs_Winterareas["year"],sum)
TR_sUDs_Winterareas$season <- "winter"

TR_sUDs_Summerareas <- subset(TR_sUDs_areas,grepl(paste0(summer, collapse = "|"), season))
TR_sUDs_Summerareas <- aggregate(TR_sUDs_Summerareas["area"],TR_sUDs_Summerareas["year"],sum)
TR_sUDs_Summerareas$season <- "summer"

TR_sUDs_WS <- rbind(TR_sUDs_Winterareas,TR_sUDs_Summerareas)


pTR_SumWin = ggplot(TR_sUDs_WS, aes(x = year, y = area, color = season)) +
  geom_line()  + xlab('Years') +
  ylab('Area (km^2)') + theme_bw() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + theme(        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  scale_x_continuous(breaks = seq(min(TR_sUDs_Winterareas$year), max(TR_sUDs_Winterareas$year), by = 1)) +
   ggtitle("Roman 50% UD Seasonal Areas X Year")

pTR_SumWin$labels$colour <- "Season"
```



